%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{amsmath} 
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \text{#1} & #2 \\
      \textbf{\small#3} & \textbf{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeExperienceheading}[2]{ % Only takes two arguments
  \item
  \text{#1} \hfill #2
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Onyekachukwu Franklin Muoghalu} \\ \vspace{1pt}
    \small 713-614-9695 $|$ \href{mailto:franklinmuoghalu@gmail.com}{\underline{franklinmuoghalu@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/onyekachukwu-muoghalu-a059aa217/}{\underline{linkedin.com/in/-franklin}} $|$
    \href{https://github.com/MFO246810}{\underline{github.com/MFO2468}} $|$
    \href{https://www.frmu.org/}{\underline{www.frmu.org}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Houston}{Houston, TX}
      {Bachelor of Science, Computer Science}{Expected Graduation: May 2026}
      \resumeItemListStart
        \resumeItem{Cumulative GPA of 3.57/4.0; Dean's list student}
      \resumeItemListEnd
  \resumeSubHeadingListEnd \vspace{-17pt}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{:Python, C/C++, C\#, Razor, JavaScript, HTML/CSS, R, Java, SQL} \\
     \textbf{Frameworks}{: React, Node.js, Flask, .NET} \\
     \textbf{Developer Tools}{: Git, Google Cloud Platform, VS Code, Visual Studio, PyCharm} \\
     \textbf{AI \& Machine Learning: }{NLP, OpenAI API (Embedding Models, GPT Models), LLM Integration, RAG Models}
    }}
 \end{itemize} \vspace{-22pt}
%-----------EXPERIENCE-----------
\section{Work Experience} 
  \resumeSubHeadingListStart
    \resumeExperienceheading
      {{\bfseries Tutor}, Scholars Enrichment Programs, University of Houston}{January 2024 -- Present} \vspace{-6pt}
      \resumeItemListStart
        \resumeItem{Provided 1:1 detailed instructions to 4+ students weekly on calculus, and data structures}
        \resumeItem{Developed customized study plans resulting in a 25\% increase in grade improvement}
      \resumeItemListEnd \vspace{-7pt}
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Project Experience }
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Syallabi-buddy} $|$ {Python, Flask, HTML, CSS, JavaScript, LLM, NLP}}{August 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Built a full-stack web application using Flask backend and integrated Google Calendar API for event scheduling.}
            \resumeItem{Automated syllabus parsing to extract key dates and assignments, adding them directly to users' calendars.}
            \resumeItem{Designed a user-friendly interface for uploading syllabi and customizing calendar updates.}
          \resumeItemListEnd \vspace{-7pt}
    \resumeProjectHeading
          {\textbf{F.I.N.D} $|$ {Python, LLM, Embedding Models, NLP, AWS polly, ChromaDB}}{January 2025}
          \resumeItemListStart
            \resumeItem{Received an Honorable mention at the Texas A\&M Hackathon (TAMUHACK) for co developing the Fast Information Navigation through Documents i.e F.I.N.D}
            \resumeItem{Developed as an AI agent that uses documents given by the user to answer queries from the user.}
            \resumeItem{Uses amazon web services to allow communication between the user and the agent}
            \resumeItem{Used the Arize software to boost efficiency of the agent by 50\% }
          \resumeItemListEnd \vspace{-7pt}
    \resumeProjectHeading
          {\textbf{O.M.N.I} $|$ {Python, LLM, Embedding Models, NLP, Open-AI}}{November 2024}
          \resumeItemListStart
            \resumeItem{Won the grand prize at the Johnson space center Hackathon(JSC Hack) for co developing the Operational Manual Navigation Interface i.e O.M.N.I}
            \resumeItem{Developed as an AI-agent with Python as the back-end and Tikinter as the front-end to assist astronauts doing space exploration during emergencies.}
            \resumeItem{Designed another program to process space shuttle manuals and create embedding vectors for a vector database.}
        \resumeItemListEnd \vspace{-7pt}
    \resumeProjectHeading
          {\textbf{Personal Web and Game Server Development} $|$ {Node.js, Nginx,}}{October 2024}
          \resumeItemListStart
            \resumeItem{Built and managed server infrastructure for hosting 5+ websites and game servers.}
            \resumeItem{Set up and configured a secure web server using Nginx, Cloudflare SSL, and Node.js backend.}
            \resumeItem{Deployed the server on both Windows and Linux environments, customizing Nginx configurations for each platform.}
          \resumeItemListEnd \vspace{-7pt}   
    \resumeProjectHeading
          {\textbf{Simulating Clocktimes} $|$ {C++}}{September 2024}
          \resumeItemListStart
            \resumeItem{Simulated CPU and user process scheduling using a priority queue, differentiating between high-priority and low-priority events.}
            \resumeItem{Designed event-driven mechanisms to handle time slices, user interactions, and SSD operations in real-time.}
            \resumeItem{Implemented time-sharing logic to ensure equitable CPU allocation among processes, improving system responsiveness by 20\%.}
            \resumeItem{Utilized C++ to build the simulation, incorporating process management, queues, and event handling.}
            \resumeItem{Tested and validated the simulation with various input scenarios to ensure accurate and reliable performance.}
        \resumeItemListEnd \vspace{-7pt}
    \resumeSubHeadingListEnd
\section{Leadership Experience}
\resumeSubHeadingListStart
    \resumeExperienceheading
      {{\bfseries Director of Tutoring}, Cougar CS, University of Houston}{January 2025 -- Present}
      \vspace{-7pt}
    \resumeExperienceheading
      {{\bfseries Events Coordinator}, Cougar AI, University of Houston}{January 2025 -- Present}
  \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------



%-------------------------------------------
\end{document}
